Impacts of Month, Grocery Vendor, Presale Prices, and Average Historical Pricing on Discounted Egg Dozen Prices

### 2024-12-14 paper/paper.qmd
combined graphs into 1 image, title edits

---
title: "Impacts of Month, Grocery Vendor, Presale Prices, and Historical Pricing on Discounted Egg Dozen Prices"
subtitle: "Cheapest Discounted Prices Are Offered by T&T or in April, by Multiple Linear Regression"
author: Cher Ning-Li
thanks: "Code and data are available at: [https://github.com/cher-ning/cndgrocers](https://github.com/cher-ning/cndgrocers)."
date: today
date-format: long
abstract: "This study aims to understand the impacts of month, vendor, presale price, and average historical item pricing on the current discounted price of egg dozens using data of sales held between March and November 2024 by the 8 major grocery vendors of Canada. Using a multiple linear regression model, these factors were found to have significant interactions with the discounted price of eggs, with T&T and April observing the lowest prices within each of their own categories. These findings are key to understanding pricing patterns of different vendors across different months, helping consumers and retailers make better informed decisions."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(arrow)
library(here)
library(ggplot2)
#library(modelsummary)
#library(rstanarm)
library(knitr)
library(kableExtra)
library(jtools)

@@

Evidently, the price of eggs has crucial impact on the lives of a huge number of people, whether it be all the consumers who are purchasing eggs regularly, or the farmers who make their living by selling this product. Between these two parties is the vendors, who determine the price at which these staple food items are sold to customers for. Therefore, it would be beneficial to understand the underlying factors that determine egg pricing at various vendors.

@@

The dataset was downloaded as two separate csv files titled `hammer-4-product.csv` and `hammer-4-raw.csv`. The `product` table includes information about specific products that are available across the different grocers, with unique product ID numbers to identify each listing at each grocer. The `raw` table includes the price and more time-specific information regarding each product's listing. The two tables were joined by matching the product IDs to create the full dataset, a comprehensive table where each entry holds all the necessary product and listing information.

>>>>

---
title: "Impacts of Month, Grocery Vendor, Presale Prices, and Average Historical Pricing on Discounted Egg Dozen Prices"
subtitle: "Cheapest Discounted Prices Are Offered by T&T and in April, by Multiple Linear Regression"
author: Cher Ning-Li
thanks: "Code and data are available at: [https://github.com/cher-ning/cndgrocers](https://github.com/cher-ning/cndgrocers)."
date: today
date-format: long
abstract: "This study aims to understand the impacts of month, vendor, presale price, and average historical item pricing on the current discounted price of egg dozens using data of sales held between March and November 2024 by the 8 major grocery vendors of Canada. Using a multiple linear regression model, these factors were found to have significant interactions with the discounted price of eggs, with T&T and April observing the lowest prices within each of their own categories. These findings are key to understanding pricing patterns of different vendors across different months, helping consumers and retailers make better informed decisions."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(arrow)
library(here)
library(ggplot2)
library(knitr)
library(kableExtra)
library(jtools)

@@

Evidently, the price of eggs impacts the lives of a huge number of people, whether it be all the consumers who are purchasing eggs regularly, or the farmers who make their living by selling this product. Between these two parties is the vendors, who determine the price at which these staple food items are sold to customers for. Therefore, it would be beneficial to understand the underlying factors that determine egg pricing at various vendors.

@@

The dataset was downloaded as two separate csv files titled `hammer-4-product.csv` and `hammer-4-raw.csv`. The `product` table includes information about specific products that are available across the different grocers, with unique product ID numbers to identify each listing at each grocer. The `raw` table includes the price and more time-specific information regarding each product's listing. The two tables were joined by matching the product IDs to create the full dataset.
